---
title: "Titanic_Analysis"
author: "Harshita Das"
date: "22/11/2020"
output:
  html_document: default
  pdf_document: default
---

# Installing Packages
install.packages("ggplot2")
install.packages("dplyr")
install.packages("GGally")
install.packages("rpart")
install.packages("rpart.plot")
install.packages("randomForest")
install.packages("knitr")

# Loading packages
library(ggplot2)
library(dplyr)
library(GGally)
library(rpart)
library(rpart.plot)
library(randomForest)
library(knitr)   

#setting working directory
setwd("C:/Users/Harshita/Desktop/Datasets/Titanic")

#reading data from test and train sets
titanic.train=read.csv(file="train.csv", stringsAsFactors = TRUE, header = TRUE)
titanic.test=read.csv(file="test.csv", stringsAsFactors = TRUE, header = TRUE)

titanic.train$IsTrainSet <- TRUE
titanic.test$IsTrainSet <- FALSE
ncol(titanic.test)
ncol(titanic.train)

titanic.test$Survived <- NA

#joining the two datasets
titanic.full <- rbind(titanic.train, titanic.test)

titanic.full[titanic.full$Embarked=='', "Embarked"] <- 'S'
table(titanic.full$Embarked)

#checking number of missing age values
table(is.na(titanic.full$Age))
age_median <- median(titanic.full$Age, na.rm=TRUE)
titanic.full[is.na(titanic.full$Age), "Age"] <- age_median

#checking number of missing fare values
table(is.na(titanic.full$Fare))
fare_median <- median(titanic.full$Fare, na.rm=TRUE)
titanic.full[is.na(titanic.full$Fare), "Fare"] <- fare_median

#splitting again into train and test data
titanic.train <- titanic.full[titanic.full$IsTrainSet==TRUE,]
titanic.test <- titanic.full[titanic.full$IsTrainSet==FALSE,]

#categotical casting
titanic.full$Pclass <- as.factor(titanic.full$Pclass)
titanic.full$Sex <- as.factor(titanic.full$Sex)
titanic.full$Embarked <- as.factor(titanic.full$Embarked)
titanic.full$Survived <- as.factor(titanic.full$Survived)
titanic.full$Age <- as.factor(titanic.full$Age)
titanic.full$SibSp <- as.factor(titanic.full$SibSp)
titanic.full$Parch <- as.factor(titanic.full$Parch)
titanic.full$Fare <- as.factor(titanic.full$Fare)


LT=dim(titanic.train)[1]

#```{r}
# All defaults
#ggplot(data=titanic.full[1:LT,],aes(x=Sex,fill=Survived))+geom_bar()
#```

```{r}
ggplot(data = titanic.full[1:LT,],aes(x=Embarked,fill=Survived))+geom_bar(position="fill")+ylab("Frequency")
```

```{r}
ggplot(data = titanic.full[1:LT,],aes(x=Pclass,fill=Survived))+geom_bar(position="fill")+ylab("Frequency")
```

```{r}
ggplot(data = titanic.full[1:LT,],aes(x=Embarked,fill=Survived))+geom_bar(position="fill")+facet_wrap(~Pclass)
```

```{r}
ggplot(data = titanic.full[1:LT,],aes(x=Embarked,fill=Survived))+geom_bar(position="fill")+facet_wrap(~Sex)
```

```{r}
ggplot(data = titanic.full[1:LT,],aes(x=Pclass,fill=Survived))+geom_bar(position="fill")+facet_wrap(~Sex)
```

```{r}
ggplot(data = titanic.full[1:LT,],aes(x=SibSp,fill=Survived))+geom_bar()
```

```{r}
ggplot(data = titanic.full[1:LT,],aes(x=Parch,fill=Survived))+geom_bar()
```


titanic.full$Title <- gsub('(.*, )|(\\..*)', '', titanic.full$Name)
titanic.full$Title[titanic.full$Title == 'Mlle']<- 'Miss' 
titanic.full$Title[titanic.full$Title == 'Ms']<- 'Miss'
titanic.full$Title[titanic.full$Title == 'Mme']<- 'Mrs' 
titanic.full$Title[titanic.full$Title == 'Lady']<- 'Miss'
titanic.full$Title[titanic.full$Title == 'Dona']<- 'Miss'

officer<- c('Capt','Col','Don','Dr','Jonkheer','Major','Rev','Sir','the Countess')

titanic.full$Title[titanic.full$Title %in% officer]<-'Officer'

titanic.full$Title<- as.factor(titanic.full$Title)

```{r}
ggplot(data = titanic.full[1:LT,],aes(x=Title,fill=Survived))+geom_bar(position="fill")+ylab("Frequency")
```